---
title: "Assignment 5"
author: "Cameron Kalik"
subtitle: Tidyverse Dplyr Cheatsheet
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
---


```{r setup, include = FALSE}
library(readr)
df1 <- read_csv("../Data/covid-variants.csv")
#To view current working directory: ("") and hit tab to view files
#To view one directory above: ("../") --> hit tab to view files
na.omit(df1)
covidVariants <- df1[seq(1, nrow(df1), 1000),] #data frame contains every 100th row of original dataset
#101 rows, 6 columns
library(tidyverse)

```

# Data
Here is the head of the `covidVariants` data frame for reference!
```{r data frame}
head(covidVariants)
```



# Select and Filter

### Filter
`filter` selects **rows** from a data frame based on a _logical condition_.
```{r filter}
covidVariants_alpha <- covidVariants %>%
  filter(variant == "Alpha") 
covidVariants_alpha
```

### Select
`select()` selects **columns** from a data frame based on _indecies or column names_.

```{r select}
covidVariants_perc <- covidVariants %>%
  select(1:3, perc_sequences)
covidVariants_perc
```

# Mutate

`mutate()` used by itself **_adds_** an existing variable to your data frame based on some condition.

```{r mutate}
covidVariants_doubleTotal <- covidVariants %>%
  mutate(doubleTotal = 2 * num_sequences_total)
covidVariants_doubleTotal
```


### Variations of Mutate
There are variations of mutate, which are:

* `mutate_at()` mutates columns at certain indecies or with certain names
* `mutate_all()` mutates all columns in data frame
* `mutate_if()` mutates columns that fulfill a certain condition

Instead of **_adding_** an existing variable to the data frame, these variations simply *__change__* the columns specified by the function.

```{r mutate variations}
covidVariants_mutated <- covidVariants %>%
  mutate_at(vars(1,3), list(factor)) %>%
  mutate_if(is.numeric, scale) 
covidVariants_mutated
```

# Summarize

### Summarize by itself

`summarize()` by itself forms a **_new_** data frame where each column contains a summary statistic of the data.

```{r summarize}
covidVariants_summary <- covidVariants %>%
  summarize(meanTotalSequences = mean(num_sequences_total), standardDeviationTotalSequences = sd(num_sequences_total))
covidVariants_summary
```

### Summarize with group_by
If `summarize()`is used in conjunction with `group_by()`, the specified statistics are computed for **_each level_** of the group specified.

```{r}
covidVariants_summary <- covidVariants %>%
  group_by(variant) %>%
  summarize(meanTotalSequences = mean(num_sequences_total), standardDeviationTotalSequences = sd(num_sequences_total))
covidVariants_summary
```

# Other dplyr functions

Other useful dplyr functions include:

* `arrange()` orders rows in a data frame by the values of a column
* `rename()`  renames columns
* `n_distinct()` finds the number of distinct entries in a certain column

```{r other functions}
covidVariants_other <- covidVariants %>%
  rename(Country = location) %>%
  arrange(desc(num_sequences_total)) 
covidVariants_other

n_distinct(covidVariants$variant)

```

**_All done!_**


